Optimal (Multiway) Spatial Joins

### 2024-05-25 msj.tex
yufei

Construct
\myeqn{
    R_i' &=& \set{r' \mid r \in R_i \text{ and its trimmed rectangle $r'$ exists}}. \nn
}
Computing the ``segment $h_1$'' for each $r \in R_i$ is an instance of Problem $\mathscr{D}$ (the find-lowest version). By symmetry, so is the computation of $h_2, v_1$, and $v_2$ segments for each $r \in R_i$. It thus follows from Section~\ref{sec:bricks} that $R_1', R_2', ..., R_{k-2}'$ can be produced in $O(n \log n)$ total time.

@@

Finding the $\cross_H(r^*)$ sets of all $r^* \in R^*_i$ is an instance of the find-all-sorted version of Problem $\mathscr{D}$. Statement (1) of Lemma~\ref{lmm:hv:type1:cross-r*}, as well as the discussion in Section~\ref{sec:bricks}, assures us that the total time to do so for all $R^*_1, ..., R^*_{k-2}$ is bounded by $O(n \log n + \out)$. Note that, for each $\cross_H(r^*)$ computed, the (horizontal) segments therein has been sorted in ascending order of y-coordinate.

>>>>

Construct
\myeqn{
    R_i' &=& \set{r' \mid r \in R_i \text{ and its trimmed rectangle $r'$ exists}}. \nn
}
Computing the ``segment $h_1$'' for each $r \in R_i$ is an instance of Problem $\mathscr{D}$ (the find-lowest version, with $H$ and $R_i$ as the input). By symmetry, so is the computation of $h_2, v_1$, and $v_2$ segments for each $r \in R_i$. It thus follows from Section~\ref{sec:bricks} that $R_1', R_2', ..., R_{k-2}'$ can be produced in $O(n \log n)$ total time.

@@

Finding the $\cross_H(r^*)$ sets of all $r^* \in R^*_i$ is an instance of the find-all-sorted version of Problem $\mathscr{D}$ (with $H$ and $R^*_i$ as the input). Statement (1) of Lemma~\ref{lmm:hv:type1:cross-r*}, as well as the discussion in Section~\ref{sec:bricks}, assures us that the total time to do so for all $R^*_1, ..., R^*_{k-2}$ is bounded by $O(n \log n + \out)$. Note that, for each $\cross_H(r^*)$ computed, the (horizontal) segments therein has been sorted in ascending order of y-coordinate.
